\begin{abstract}
This report presents the development of an intelligent recipe recommendation and generation system using deep learning techniques. The system, named NutriWise, employs two specialized machine learning models: a classification model for recipe recommendation and a generation model for personalized recipe creation. 

The classification model uses a deep neural network architecture with 1,266,880 parameters, achieving target accuracy above 75\% for recommending recipes from a dataset of 8,000 recipes. The generation model, with 763,136 parameters, generates personalized recipes based on available ingredients and user preferences.

Both models are implemented using TensorFlow/Keras framework and trained on a comprehensive dataset of 8,000 recipes with 137-dimensional feature vectors. The system demonstrates the effectiveness of deep learning approaches in food recommendation systems, providing users with personalized culinary experiences.

\keywordss{Machine Learning, Deep Neural Networks, Recipe Recommendation, Food Generation, TensorFlow, Classification}
\end{abstract}

\begin{abstract}
Ce rapport présente le développement d'un système intelligent de recommandation et de génération de recettes utilisant des techniques d'apprentissage profond. Le système, nommé NutriWise, emploie deux modèles d'apprentissage machine spécialisés : un modèle de classification pour la recommandation de recettes et un modèle de génération pour la création de recettes personnalisées.

Le modèle de classification utilise une architecture de réseau de neurones profond avec 1,266,880 paramètres, atteignant une précision cible supérieure à 75\% pour recommander des recettes parmi un dataset de 8,000 recettes. Le modèle de génération, avec 763,136 paramètres, génère des recettes personnalisées basées sur les ingrédients disponibles et les préférences utilisateur.

Les deux modèles sont implémentés en utilisant le framework TensorFlow/Keras et entraînés sur un dataset complet de 8,000 recettes avec des vecteurs de features de 137 dimensions. Le système démontre l'efficacité des approches d'apprentissage profond dans les systèmes de recommandation alimentaire, offrant aux utilisateurs des expériences culinaires personnalisées.

\keywords{Apprentissage Machine, Réseaux de Neurones Profonds, Recommandation de Recettes, Génération Alimentaire, TensorFlow, Classification}
\end{abstract}

